Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-29 article.tex
typo

Afterwards, we have computed the difference between $s_{i,j}$ and
$s_{j,i}$, that we call $z_{i,j}$, and used this difference to modify  $p_{i,j}$ and
$p_{i,j}$ so as to take into account directionality. Naturally, îf
$z_{i,j}$ is greater  (smaller) than $0$, we may conclude that should there  be an
edge between $i$ and $j$, then this edge would have to be oriented
from $i$ to $j$ ($j$ to $i$).

>>>>

Afterwards, we have computed the difference between $s_{i,j}$ and
$s_{j,i}$, that we call $z_{i,j}$, and used this difference to modify  $p_{i,j}$ and
$p_{i,j}$ so as to take into account directionality. Naturally, if
$z_{i,j}$ is greater  (smaller) than $0$, we may conclude that should there  be an
edge between $i$ and $j$, then this edge would have to be oriented
from $i$ to $j$ ($j$ to $i$).
